The Concurrent Calculi Formalisation Benchmark\\{\normalsize(Talk Proposal)

### 2023-07-12 talk-proposal/talk-proposal.tex
Remove a redundant sentence.

\section{Design of the challenge}
Our challenge problems cannot address every technique and subfield at once.
We have identified three key aspects fundamental to mechanisations of concurrent calculi and designed our challenge problems to exercise these.
Like previous benchmark authors, we would like to stress that our challenge is not meant to be comprehensive: applications such as multiparty session types, choreographies, conversation types and psi-calculi are not directly covered by our challenge problems.
Most applications will however still need the basic techniques that our challenge problems exercise.

>>>>

\section{Design of the challenge}
We have identified three key aspects fundamental to mechanisations of concurrent calculi and designed our challenge problems to exercise these.
Like previous benchmark authors, we would like to stress that our challenge is not meant to be comprehensive: applications such as multiparty session types, choreographies, conversation types and psi-calculi are not directly covered by our challenge problems.
Most applications will however still need the basic techniques that our challenge problems exercise.
